Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles

### 2015-08-22 paper.tex
title

\title{Author disambiguation of large-scale semi-labeled collections of scientific articles}

@@

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available
online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.  Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
of a linkage function and of SciPy \citep{scipy} for clustering. All
components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
understand and reuse.

\glnote{Not sure we should talk about parallelization?}
\glnote{Mention (future) deployment in Inspire?}

% Performance-wise, the clustering step appeared to be the bottleneck. We improved the
% algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
% semi-supervised clustering for $n$ different blocks in the same moment. In the production
% systems the disambiguation often need not be run on the whole dataset. Once the dataset has
% been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
% signatures arrive in the digital library. First of all, the similarity function can be
% reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
% contained within.

@@

\textit{Normalization.} As discussed before, the seemingly anodyne step of
normalizing author names (stripping accents, removing affixes), as done in the
baseline, reveals to be quite significant. Results of Table~\ref{table:results}
indeed clearly suggests that not normalizing significantly reduces performance
(yielding an F-measure of $0.9830$ when normalizing, but decreasing to $0.9791$
when raw author name strings are used instead).

>>>>

\title{Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles}

@@

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available
online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.  Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
of a linkage function and of SciPy \citep{scipy} for clustering. All
components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
understand and reuse. Our implementation is made to be efficient, exploiting
parallelization when available, making it ready for production environments.

@@

\textit{Name normalization.} As discussed before, the seemingly anodyne step of
normalizing author names (stripping accents, removing affixes), as done in the
baseline, reveals to be quite significant. Results of Table~\ref{table:results}
indeed clearly suggests that not normalizing significantly reduces performance
(yielding an F-measure of $0.9830$ when normalizing, but decreasing to $0.9791$
when raw author name strings are used instead).
